---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
h2 {
  color: #003366;
  font-family: Arial, sans-serif;
  border-bottom: 2px solid #ccc;
  padding-bottom: 5px;
  margin-top: 30px;
}

p {
  font-size: 15px;
  line-height: 1.6;
  color: #333;
}

body {
  background-color: #f9f9f9;
  padding: 20px;
}
```

## What's going on with this data?

### Insights from Daily Watch Time
The most frequently recorded watch duration is **5 hours**, suggesting a trend of extended video engagement among users.Several sessions also fall into the **2 to 6 hour** range, indicating moderate to high usage patterns.Longer sessions like **7 or 8 hours** are rare, but they may represent users who leave content playing for extended periods, such as overnight or while multitasking.Overall, the distribution suggests that many users spend a significant portion of their day consuming video content.

### Summary of Watch Time
A total of **26** video-watching sessions were recorded.The **average time** spent per session was **3 hours**, and the **maximum time** spent in a single session was **8 hours**. Together, all sessions accumulated to a total of **78 hours** of video engagement.

### Insights from Video Type Distribution
The dataset reveals a wide variety of video content being watched. Among the 26 total responses, most video sessions include multiple types of content.The **most frequently selected combination** was:
- Entertainment (comedy, short skits, etc.)
- Food (cooking, mukbang, food reviews)
- Beauty/Fashion
- Educational/Informative
This suggests that users are not only watching for leisure (entertainment and food),  but also show interest in self-improvement and appearance-related content.  

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQeB7WK63CMpDPnUypKBQncLhNGM71ptHFKZvjn8D2U-F3ECc_EA-GsiEFCjWOHfO6X929R049JfS7J/pub?output=csv") 

latest_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQeB7WK63CMpDPnUypKBQncLhNGM71ptHFKZvjn8D2U-F3ECc_EA-GsiEFCjWOHfO6X929R049JfS7J/pub?output=csv") %>%
  rename(Time = 1,
         Hours_spend = 2,
         Type_of_video = 3,
         Interesting_video = 4)

length_data <- nrow(latest_data) #Calculate how many samples there are in total
print(length_data)
latest_data %>%
  select(Hours_spend) %>%
  max() #Calculate the value of the most time spent per day
sum_data <- latest_data %>%
  select(Hours_spend) %>%
  sum() #Calculate the sum of all statistics
print(sum_data)
avr_data <- sum_data / length_data #Calculate the mean by dividing the number of samples by sum
print(avr_data)

ggplot(latest_data, aes(x = Type_of_video)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Video Type Distribution", x = "Type of video", y = "Count") 
#Demonstrate the distribution of watched video content with a vertical statistical graph

ggplot(latest_data, aes(y = Hours_spend)) +
  geom_bar(fill = "orange") +
  labs(title = "Total Watch Time per Day", x = "Count", y = "hours")
#Demonstrate the distribution of video viewing time with a horizontal statistical graph

```

## Conclusion
This dynamic report explored 26 short-form video watching sessions, analyzing both the amount of time spent and the types of content consumed.Key findings include:
- The **average session length** was **3 hours**, with the **longest session lasting 8 hours**, indicating a high level of user engagement.
- The **most common session length** was 5 hours.
- Users watched a diverse range of video content. The most frequently selected combination included:
  - Entertainment
  - Food
  - Beauty/Fashion
  - Educational/Informative
This combination reflects a balance between entertainment and learning.  
It suggests that short-form video platforms are not only used for fun and relaxation, but also as a space for personal growth and lifestyle interests.Overall, the data shows that users tend to engage deeply with content, and their preferences span across both practical and recreational categories.
